|

### 2024-10-29 output/seminar-slideshow.qmd
Corrects arrow direction in regression scores plot

# NOTE: Manual call to qgraph:
edge_list <- tribble(
  ~rhs, ~lhs,
  7,    1,
  7,    2,
  7,    3,
  8,    4,
  8,    5,
  8,    6,
  7,    8,
  8,    7
)
vSize <- c(10 |> rep(6), 14 |> rep(2))

>>>>

# NOTE: Manual call to qgraph:
edge_list <- tribble(
  ~rhs, ~lhs,
  1,    7,
  2,    7,
  3,    7,
  4,    8,
  5,    8,
  6,    8,
  7,    8,
  8,    7
)
vSize <- c(10 |> rep(6), 14 |> rep(2))
